---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

**Aniroop's Work:**

This analysis explores residential home sales in Ames since 2017. The distribution of SalePrice is right-skewed, with most homes selling between \$150,000 and \$350,000. Larger homes tend to sell for higher prices. We examined the relationship between living area and sale price and found a strong positive relationship.

**Inspecting the Dataset:**

```{r}
library(classdata)
library(tidyverse)

data(ames)

head(ames)
glimpse(ames)
```

The Ames dataset contains information on residential property sales in Ames, Iowa.\
The variables include both numeric and categorical types. Numerical variables measure quantities such as price and square footage, while categorical variable represent classifications like neigbhorhood or house style.


## Ewan's notes
The first lines of the dataset displays the varibles:

Parcel ID: A unique string for each property, no expected range

Address: string representing the property's address, no expected range

Occupancy: Categorical variable displaying type of occupancy in the home

Year Built: Numeric variable displaying the year the home was built, expected range 1900-2026

Acres: Numeric variable displaying the total acreage of the property, expected range 0.01 - 5

Total Living Area: Numeric variable displaying living area in square feet, expected range 400 - 5000 sf

Finished Basement Area: Numeric variable displaying finished basement area in square feet, expected range 0 - 2000

Bedrooms: Numeric variable displaying number of bedrooms, expected range 0 - 7

Lot Area: Numeric variable displaying lot area in square feet, expected range 0 - 20000 sf

AC: categorical variable displaying if there is ac or not

Fireplace: categorical variable displaying if there is a fireplace or not

Neighborhood: string representing the neighborhood the property is in

Sale date: quantitative variable representing the date the property was sold, range expected 2017 - 2026

Sale price: quantitative variable representing the price the home sold for, expected range $50,000 - $800,000

Multi sale: variable representing whether multiple properties were bought in one sale



**Step 2: Main Variable**

The main variable for this analysis is \*\*SalePrice\*\*, which represents the final selling price of a home.\
\
SalePrice is a numeric variable measured in dollars. Typical values range from around \$100,000 to over \$500,000 depending on the size, condition, and location of the home.

**Step 3: Distribution of SalePrice**

```{r}
ggplot(ames, aes(x = `Sale Price`)) +
  geom_histogram(bins = 30, fill = "steelblue", color = "white") +
  labs(
    title = "Distribution of Sale Prices",
    x = "Sale Price",
    y = "Count"
  )
```

The histogram shows that sale prices are right skewed.

**Step 4: Relationship Between Living Area and Sale Price**

```{r}
ggplot(filter(ames, `Sale Price` > 0),
       aes(x = `TotalLivingArea (sf)`, y = `Sale Price`)) +
  geom_point(alpha = 0.6) +
  labs(
    title = "Sale Price vs Living Area",
    x = "Total Living Area (sq ft)",
    y = "Sale Price"
  )
```

## Ewan's Work:
## Relationship between Year Built and Sale Price
```{r}
ames %>%
  filter(YearBuilt > 1800, `Sale Price` > 0, `Sale Price` < 1000000) %>%
  ggplot(aes(x = YearBuilt, y = `Sale Price`))+
    geom_point(alpha = 0.3) +
    labs(
      title = "Sale price vs Year Built",
      x = "Year Built",
      y = "Sale Price"
      )
```

The range of Year Built is roughly from 1880 - 2020. The data is skewed to the left with the majority of homes being newer. The graph shows a trend that newer homes tend to sell for a higher price. The y-axis is skewed to the right, meaning that the majority of homes sell for a lower price which relates to what is seen in step 3.
