---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

**Aniroop's Work:**

This analysis explores residential home sales in Ames since 2017. The distribution of SalePrice is right-skewed, with most homes selling between \$150,000 and \$350,000. Larger homes tend to sell for higher prices. We examined the relationship between living area and sale price and found a strong positive relationship.

**Inspecting the Dataset:**

```{r}
library(classdata)
library(tidyverse)

data(ames)

head(ames)
glimpse(ames)
```

The Ames dataset contains information on residential property sales in Ames, Iowa.\
The variables include both numeric and categorical types. Numerical variables measure quantities such as price and square footage, while categorical variable represent classifications like neigbhorhood or house style.

**Step 2: Main Variable**

The main variable for this analysis is \*\*SalePrice\*\*, which represents the final selling price of a home.\
\
SalePrice is a numeric variable measured in dollars. Typical values range from around \$100,000 to over \$500,000 depending on the size, condition, and location of the home.

**Step 3: Distribution of SalePrice**

```{r}
ggplot(ames, aes(x = `Sale Price`)) +
  geom_histogram(bins = 30, fill = "steelblue", color = "white") +
  labs(
    title = "Distribution of Sale Prices",
    x = "Sale Price",
    y = "Count"
  )
```

The histogram shows that sale prices are right skewed.

**Step 4: Relationship Between Living Area and Sale Price**

```{r}
ggplot(filter(ames, `Sale Price` > 0),
       aes(x = `TotalLivingArea (sf)`, y = `Sale Price`)) +
  geom_point(alpha = 0.6) +
  labs(
    title = "Sale Price vs Living Area",
    x = "Total Living Area (sq ft)",
    y = "Sale Price"
  )
```
